```{r, include=FALSE, warning=FALSE, message=FALSE}
## Load libraries.
library(boot)
library(dplyr)
```

```{r, include=FALSE, warning=FALSE, message=FALSE}
## Import functions and variables.
source('src/simulate_discordance.R', local = discordance <- new.env())
source('src/bootstrapped_ci.R', local = bootstrapped <- new.env())
source('src/comparison.R', local = comparison <- new.env())
source('src/print_table.R', local = print <- new.env())
```

## Simulate predictions and calculate % discordance.

```{r, echo=FALSE}
discordance_status <-
  discordance$simulate_bias_induced_discordance(
    parameters$data,
    parameters$identifier,
    parameters$uncertain_variables,
    parameters$bias_factors,
    parameters$bias_intercepts,
    parameters$laboratory,
    parameters$continuous_prediction_function,
    parameters$categorical_prediction_function,
    model = parameters$model,
    model_variables = parameters$model_variables,
    model_outcome = parameters$model_outcome,
    model_cut_off = parameters$model_cut_off
  )

write.csv(
  discordance_status,
  parameters$path_and_name_simulated_results,
  row.names = FALSE
)
```

## Summarise results.

-   Histogram and QQ-plot of absolute_difference_continuous_prediction:

```{r, echo=FALSE}
discordance$plot_distribution_per_laboratory(
  discordance_status, 
  "absolute_difference"
)
```

-   Histogram and QQ-plot of percentage_difference_continuous_prediction:

```{r, echo=FALSE}
discordance$plot_distribution_per_laboratory(
  discordance_status, 
  "percentage_difference"
)
```

## Calculate discordance measures,

The histograms and QQ-plots show the distribution of bootstrapped estimates and together with the bootstrap bias estimate determine the appropriateness of normal and percentile bootstrapped confidence intervals. Bias-corrected and accelerated (BCa) confidence intervals correct for bias and skewness in the distribution of bootstrapped estimates.

```{r, echo=FALSE}
bootstrapped_discordant_predictions <- 
  discordance_status %>%
  group_split(laboratory) %>%
  set_names(unique(discordance_status[["laboratory"]])) %>%
  purrr::map(
    function(x){
      boot(
        x,
        discordance$get_distribution_of_bias_measures_as_vector,
        parameters$bootstrap_number_of_samples
      )
    }
  )
```

-   Table with bootstrapped summary statistics:

```{r, echo=FALSE}
bootstrapped_ci_discordance_status <- bootstrapped$get_bootstrapped_ci_all_laboratories(
  bootstrapped_discordant_predictions,
  discordance$get_variable_names_from_distribution_of_bias_measures_as_vector(discordance_status), 
  parameters$bootstrap_confidence_level, 
  parameters$bootstrap_methods
)

write.csv(
  bootstrapped_ci_discordance_status,
  parameters$path_and_name_stats_with_ci,
  row.names = FALSE
)

print$print_table_bootstrapped_summary(bootstrapped_ci_discordance_status, 4)
```

-   Compact table with summary statistics.

```{r, echo=FALSE}
summary_discordance_status <- bootstrapped$get_dataframe_without_ci(bootstrapped_ci_discordance_status)

write.csv(
  summary_discordance_status,
  parameters$path_and_name_stats_without_ci,
  row.names = FALSE
)

print$print_table_summary(summary_discordance_status, 4)
```

-   Histogram and distribution of median absolute difference:

```{r, echo=FALSE}
histogram_absolute_difference <- comparison$get_histogram(
  summary_discordance_status, 
  "absolute_difference_median",
  "Median absolute difference",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_absolute_difference_binwidth,
  parameters$histogram_absolute_difference_x_range,
  parameters$histogram_absolute_difference_y_range
)

plot(histogram_absolute_difference)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
distribution_absolute_difference <- comparison$get_distribution_table(
  summary_discordance_status, 
  "absolute_difference_median", 
  "laboratory"
)

print$print_table_distribution(distribution_absolute_difference, 4)
```

-   Histogram and distribution of median percentage difference:

```{r, echo=FALSE}
histogram_percentage_difference <- comparison$get_histogram(
  summary_discordance_status, 
  "percentage_difference_median",
  "Percentage absolute difference",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_percentage_difference_binwidth,
  parameters$histogram_percentage_difference_x_range,
  parameters$histogram_percentage_difference_y_range
)

plot(histogram_percentage_difference)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
distribution_percentage_difference <- comparison$get_distribution_table(
  summary_discordance_status, 
  "percentage_difference_median", 
  "laboratory"
)

print$print_table_distribution(distribution_percentage_difference, 4)
```

-   Histogram and distribution of percentage discordant:

```{r, echo=FALSE}
histogram_percentage_discordant <- comparison$get_histogram(
  summary_discordance_status, 
  "percentage_discordant",
  "Percentage discordant",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_percentage_discordant_binwidth,
  parameters$histogram_percentage_discordant_x_range,
  parameters$histogram_percentage_discordant_y_range
)

plot(histogram_percentage_discordant)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
distribution_percentage_discordant <- comparison$get_distribution_table(
  summary_discordance_status, 
  "percentage_discordant", 
  "laboratory"
)

print$print_table_distribution(distribution_percentage_discordant, 4)
```

```{r, echo=FALSE}
## Save plots.
saveRDS(histogram_absolute_difference, parameters$path_and_name_histogram_absolute_difference)
saveRDS(histogram_absolute_difference, parameters$path_and_name_histogram_percentage_difference)
saveRDS(histogram_absolute_difference, parameters$path_and_name_histogram_percentage_discordant)
```
