```{r, include=FALSE, warning=FALSE, message=FALSE}
## Load libraries.
library(boot)
library(dplyr)
```

```{r, include=FALSE, warning=FALSE, message=FALSE}
## Import functions and variables.
source('src/calculate_bias_table.R', local = bias <- new.env())
source('src/simulate_discordance.R', local = discordance <- new.env())
source('src/bootstrapped_ci.R', local = bootstrapped <- new.env())
source('src/comparison.R', local = comparison <- new.env())
source('src/print_table.R', local = print <- new.env())
source('src/save_output.R', local = save <- new.env())
```

```{r, echo=FALSE}
## Prepare bias data.
bias_tables <- bias$get_bias_table(
  parameters$bias_data,
  parameters$bias_data_ref_ptp,
  parameters$bias_data_names,
  parameters$model_variables[!parameters$model_variables %in% parameters$uncertain_variables]
)

bias_intercepts <- bias_tables$intercepts
bias_factors <- bias_tables$slopes
```

## Simulate predictions and calculate % discordance.

```{r, echo=FALSE}
discordance_status <-
  discordance$simulate_bias_induced_discordance(
    parameters$data,
    parameters$identifier,
    parameters$uncertain_variables,
    bias_factors,
    bias_intercepts,
    parameters$laboratory,
    parameters$continuous_prediction_function,
    parameters$ordinal_prediction_function,
    parameters$categorical_prediction_function,
    parameters$path_output,
    model = parameters$model,
    model_variables = parameters$model_variables
  )


save$save_summary(
  discordance_status, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population,
  "bias_per_individual"
)
```

## Calculate discordance measures,

The distribution of bootstrapped estimates and the bootstrap bias estimate determine the appropriateness of normal and percentile bootstrapped confidence intervals. Bias-corrected and accelerated (BCa) confidence intervals correct for bias and skewness in the distribution of bootstrapped estimates but require more computational time.

```{r, echo=FALSE}
bootstrapped_discordant_predictions <- 
  discordance_status %>%
  group_split(laboratory) %>%
  set_names(unlist(group_keys(discordance_status %>% group_by(laboratory)))) %>%
  purrr::map(
    function(x){
      boot(
        x,
        discordance$get_summary_of_discordance_measures_as_vector,
        parameters$bootstrap_number_of_samples
      )
    }
  )
```

-   Table with bootstrapped summary statistics:

```{r, echo=FALSE}
bootstrapped_ci_discordance_status <- bootstrapped$get_bootstrapped_ci_all_laboratories(
  bootstrapped_discordant_predictions,
  discordance$get_variable_names_from_summary_of_discordance_measures_as_vector(discordance_status), 
  parameters$bootstrap_confidence_level, 
  parameters$bootstrap_methods
)

save$save_summary(
  bootstrapped_ci_discordance_status, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population,
  "stats_with_ci"
)

print$print_table_bootstrapped_summary(bootstrapped_ci_discordance_status, 4)
```

-   Compact table with summary statistics.

```{r, echo=FALSE}
summary_discordance_status <- bootstrapped$get_dataframe_without_ci(bootstrapped_ci_discordance_status)

save$save_summary(
  summary_discordance_status, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population,
  "stats_without_ci"
)

print$print_table_summary(summary_discordance_status, 4)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of median prediction for continuous predictions:")

histogram_continuous_median_prediction <- comparison$get_histogram(
  summary_discordance_status, 
  "continuous_median_prediction",
  "Median continuous prediction",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_continuous_median_prediction_binwidth,
  parameters$histogram_continuous_median_prediction_x_range,
  parameters$histogram_continuous_median_prediction_y_range
)

save$save_histogram(
  histogram_continuous_median_prediction, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_continuous_median_prediction)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_continuous_median_prediction <- comparison$get_distribution_table(
  summary_discordance_status, 
  "continuous_median_prediction", 
  "laboratory"
)

print$print_table_distribution(distribution_continuous_median_prediction, 4)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of median difference for continuous predictions:")

histogram_continuous_median_difference <- comparison$get_histogram(
  summary_discordance_status, 
  "continuous_median_difference",
  "Median difference",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_continuous_median_difference_binwidth,
  parameters$histogram_continuous_median_difference_x_range,
  parameters$histogram_continuous_median_difference_y_range
)

save$save_histogram(
  histogram_continuous_median_difference, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_continuous_median_difference)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_continuous_median_difference <- comparison$get_distribution_table(
  summary_discordance_status, 
  "continuous_median_difference", 
  "laboratory"
)

print$print_table_distribution(distribution_continuous_median_difference, 4)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of median percentage difference prediction for continuous predictions:")

histogram_continuous_median_percentage_difference <- comparison$get_histogram(
  summary_discordance_status, 
  "continuous_median_percentage_difference",
  "Median percentage difference",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_continuous_median_percentage_difference_binwidth,
  parameters$histogram_continuous_median_percentage_difference_x_range,
  parameters$histogram_continuous_median_percentage_difference_y_range
)

save$save_histogram(
  histogram_continuous_median_percentage_difference, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_continuous_median_percentage_difference)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_continuous_median_percentage_difference <- comparison$get_distribution_table(
  summary_discordance_status, 
  "continuous_median_percentage_difference", 
  "laboratory"
)

print$print_table_distribution(distribution_continuous_median_percentage_difference, 4)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of mean absolute error for continuous predictions:")

histogram_continuous_mae <- comparison$get_histogram(
  summary_discordance_status, 
  "continuous_mae",
  "Mean absolute error",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_continuous_mae_binwidth,
  parameters$histogram_continuous_mae_x_range,
  parameters$histogram_continuous_mae_y_range
)

save$save_histogram(
  histogram_continuous_mae, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_continuous_mae)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_continuous_mae <- comparison$get_distribution_table(
  summary_discordance_status, 
  "continuous_mae", 
  "laboratory"
)

print$print_table_distribution(distribution_continuous_mae, 4)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of root mean squared error (rmse) for continuous predictions:")

histogram_continuous_rmse <- comparison$get_histogram(
  summary_discordance_status, 
  "continuous_rmse",
  "Root mean squared error",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_continuous_rmse_binwidth,
  parameters$histogram_continuous_rmse_x_range,
  parameters$histogram_continuous_rmse_y_range
)

save$save_histogram(
  histogram_continuous_rmse, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_continuous_rmse)
```

```{r, eval = is.function(parameters$continuous_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_continuous_rmse <- comparison$get_distribution_table(
  summary_discordance_status, 
  "continuous_rmse", 
  "laboratory"
)

print$print_table_distribution(distribution_continuous_rmse, 4)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of median difference for ordinal predictions:")

histogram_ordinal_median_difference <- comparison$get_histogram(
  summary_discordance_status, 
  "ordinal_median_difference",
  "Median difference",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_ordinal_median_difference_binwidth,
  parameters$histogram_ordinal_median_difference_x_range,
  parameters$histogram_ordinal_median_difference_y_range
)

save$save_histogram(
  histogram_ordinal_median_difference, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_ordinal_median_difference)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_ordinal_median_difference <- comparison$get_distribution_table(
  summary_discordance_status, 
  "ordinal_median_difference", 
  "laboratory"
)

print$print_table_distribution(distribution_ordinal_median_difference, 4)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of mean_absolute_error for ordinal predictions:")

histogram_ordinal_mae <- comparison$get_histogram(
  summary_discordance_status, 
  "ordinal_mae",
  "Mean absolute error",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_ordinal_mae_binwidth,
  parameters$histogram_ordinal_mae_x_range,
  parameters$histogram_ordinal_mae_y_range
)

save$save_histogram(
  histogram_ordinal_mae, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_ordinal_mae)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_ordinal_mae <- comparison$get_distribution_table(
  summary_discordance_status, 
  "ordinal_mae", 
  "laboratory"
)

print$print_table_distribution(distribution_ordinal_mae, 4)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of micro-averaged root mean squared error for ordinal predictions:")

histogram_ordinal_micro_rmse <- comparison$get_histogram(
  summary_discordance_status, 
  "ordinal_micro_rmse",
  "Micro-averaged root mean squared error",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_ordinal_micro_rmse_binwidth,
  parameters$histogram_ordinal_micro_rmse_x_range,
  parameters$histogram_ordinal_micro_rmse_y_range
)

save$save_histogram(
  histogram_ordinal_micro_rmse, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_ordinal_micro_rmse)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_ordinal_micro_rmse <- comparison$get_distribution_table(
  summary_discordance_status, 
  "ordinal_micro_rmse", 
  "laboratory"
)

print$print_table_distribution(distribution_ordinal_micro_rmse, 4)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of macro-averaged root mean squared error for ordinal predictions:")

histogram_ordinal_macro_rmse <- comparison$get_histogram(
  summary_discordance_status, 
  "ordinal_macro_rmse",
  "Macro-averaged root mean squared error",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_ordinal_macro_rmse_binwidth,
  parameters$histogram_ordinal_macro_rmse_x_range,
  parameters$histogram_ordinal_macro_rmse_y_range
)

save$save_histogram(
  histogram_ordinal_macro_rmse, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_ordinal_macro_rmse)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_ordinal_macro_rmse <- comparison$get_distribution_table(
  summary_discordance_status, 
  "ordinal_macro_rmse", 
  "laboratory"
)

print$print_table_distribution(distribution_ordinal_macro_rmse, 4)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of percentage discordant for ordinal predictions:")

histogram_ordinal_percentage_discordant <- comparison$get_histogram(
  summary_discordance_status, 
  "ordinal_percentage_discordant",
  "Percentage discordant",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_ordinal_percentage_discordant_binwidth,
  parameters$histogram_ordinal_percentage_discordant_x_range,
  parameters$histogram_ordinal_percentage_discordant_y_range
)

save$save_histogram(
  histogram_ordinal_percentage_discordant, 
  parameters$path_output, 
  parameters$model_name, 
  "discordance",
  parameters$population
)

plot(histogram_ordinal_percentage_discordant)
```

```{r, eval = is.function(parameters$ordinal_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_ordinal_percentage_discordant <- comparison$get_distribution_table(
  summary_discordance_status, 
  "ordinal_percentage_discordant", 
  "laboratory"
)

print$print_table_distribution(distribution_ordinal_percentage_discordant, 4)
```

```{r, eval = is.function(parameters$categorical_prediction_function), results = 'asis', echo=FALSE}
cat("* Histogram and distribution of percentage discordant for dichotomous predictions:")

histogram_dichotomous_percentage_discordant <- comparison$get_histogram(
  summary_discordance_status, 
  "dichotomous_percentage_discordant",
  "Percentage discordant",
  parameters$histogram_method,
  parameters$histogram_method_label,
  parameters$histogram_dichotomous_percentage_discordant_binwidth,
  parameters$histogram_dichotomous_percentage_discordant_x_range,
  parameters$histogram_dichotomous_percentage_discordant_y_range
)

save$save_histogram(
  histogram_dichotomous_percentage_discordant, 
  parameters$path_output, 
  parameters$model_name,
  "discordance",
  parameters$population
)

plot(histogram_dichotomous_percentage_discordant)
```

```{r, eval = is.function(parameters$categorical_prediction_function), results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
distribution_dichotomous_percentage_discordant <- comparison$get_distribution_table(
  summary_discordance_status, 
  "dichotomous_percentage_discordant", 
  "laboratory"
)

print$print_table_distribution(distribution_dichotomous_percentage_discordant, 4)
```
